\section{Relations between models}
\label{sec:spin-walk}

One way to understand universality is via representation theorems that relate
different models. For instance, the \emph{Kac-Siegert transformation}
can be used to write the partition function of the $O(n)$ model as a partition function
for a perturbation of the $|\varphi|^4$ model (we will discuss this further in
Section~\ref{sec:hard-core}). In the other direction, the
Griffiths-Simon construction \cite{SG73} can be used to approximate the $1$-component
$|\varphi|^4$ model by a sum of Ising models. Such theorems do not necessarily
imply universality
(in the sense that models related in this way have the same critical exponents or
scaling limit), but tend to be suggestive of it and may in some cases
be used as the basis for the proof of a universality-type result.

We have already noted in Example~\ref{ex:gff-asymp} the close relationship between
the simple random walk
and the Gaussian free field, which ultimately stems from the representation of
matrix powers in terms of walks and which is familiar to anyone
who has studied Markov chains. Namely, if $M$ is a $\vertices\times\vertices$
matrix, then
\begin{equation}
M^n_{ab} = \sum_{x_1,\ldots,x_n\in\vertices} M_{ax_1} M_{x_1x_2} \ldots M_{x_nb}.
\end{equation}
When $M$ is indexed by $\edges$, the
sum above can be replaced by a sum over $n$-step walks from $a$ to $b$ on $\graph$.
When the entries of $M$ are non-negative, such a sum acquires a probabilistic
interpretation as an expectation with respect to the random walk whose steps
are weighted by the entries of $M$.

It was discovered by Symanzik \cite{Syma69} that certain spin systems could be
represented as models of interacting walks in a background of interacting loops.
Symanzik used this insight to study quantum field theories in terms of walks.
Such representations were also studied, e.g.\ in \cite{BFS82,Dynk83}. A comprehensive
reference is \cite{FFS92}.

In the opposite direction, one can consider studying walks by looking for corresponding
spin systems. In \cite{Genn72}, De Gennes argued that the self-avoiding walk
corresponds to an $n \to 0$ ``limit'' of the $O(n)$ spin model and used this
to predict the values of its critical exponents. Since $n$ is
the number of components of the spins, the $O(n)$ model is only well-defined
for $n$ a positive integer and it is not clear how to make sense of such a limit.

Parisi and Sourlas \cite{PS80} and McKane \cite{McKa80} discovered
an alternative approach to the predictions of De Gennes. They argued that the weakly
self-avoiding walk two-point function could be represented as the two-point function
for a \emph{supersymmetric} version of the $|\varphi|^4$ model, involving boson and
fermion fields (we discuss these below). The formal appearance of $n = 0$ quantities
was then explained as a consequence of a symmetry between the bosons and fermions known
as \emph{supersymmetry}.

In Section~\ref{sec:ntozero}, we provide a brief description of the heuristic
relation between spin systems and self-avoiding walk. Then in Section~\ref{sec:intrep},
we describe the rigorous representation of WSAW-SA as a supersymmetric field
theory.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{The \texorpdfstring{$n\to0$}{n approaches 0} limit}
\label{sec:ntozero}

The heuristic relation between self-avoiding walk and spin systems is most easily
treated on graphs $\graph$ of degree $3$ (e.g.\ the triangular or hexagonal lattice),
so we restrict our attention to this case. In
addition, we consider the version of the $O(n)$ model with spins normalized to
lie on the sphere of radius $\sqrt n$, which we equip with the uniform measure.
We denote the product measure on the resulting configuration space by
\begin{equation}
d\sigma = \prod_{x\in\vertices} d\sigma_x.
\end{equation}

\begin{rk}
This normalization of the spins was in fact used when the $O(n)$ model was originally
introduced in \cite{Stanley68}. Moreover, in \cite{KT71}, it was shown that this
normalization is necessary for the study of the $n\to\infty$ limit.
\end{rk}

The \emph{high-temperature expansion} of a spin system is based on the expansion of the
Boltzmann weight $e^{\beta H}$ around $\beta = 0$.
For the $O(n)$ spin model witn interaction $J_{xy} = \1_{x\sim y}$, an uncontrolled
approximation of this expansion yields
\begin{align}
Z 
	&=
\int d\sigma \prod_{xy\in\edges} e^{\beta \sigma_x \cdot \sigma_y} \nonumber \\
	&\approx
\int d\sigma \prod_{xy\in\edges} (1 + \beta \sigma_x \cdot \sigma_y) \nonumber \\
	&=
\sum_{E \subset \edges} \beta^{|E|} \int d\sigma \prod_{xy \in E} \sigma_x \cdot \sigma_y
\end{align}
By reflection-invariance, the last integral above is non-zero
if and only if every vertex in the product over $E$ appears an even number of times.
On a graph of degree $3$, this is only possible if $E$ is a (possibly empty) collection
of mutually avoiding (i.e.\ disjoint) self-avoiding loops (walks from a vertex to itself
that are self-avoiding everywhere except this vertex).
% Thus, the sum over subsets of $\edges$ can be replaced by a sum over collections of such loops.

Moreover, for any loop $L$, invariance under orthogonal transformations and the fact
that spins have radius $\sqrt n$ implies that
\begin{equation}
\int d\sigma \; \prod_{xy\in L} \sigma_x \cdot \sigma_y
	=
\sum_{i=1}^n \prod_{x\in\vertices(L)} \int d\sigma_x \; (\sigma^i_x)^2
	=
n,
\end{equation}
where $\vertices(L)$ is the set of vertices in $L$.
Thus,
\begin{equation}
\label{e:loop-partition}
Z
	\approx
1
	+
\sum_{N \ge 1}
\frac{n^N}{N!}
\sum_{L_1,\ldots,L_N}
\beta^{|L_1|+\cdots+|L_N|},
\end{equation}
where the inner sum is over all collections of loops $L_1, \ldots, L_N$
and permutations of these loops are accounted for by the $1/N!$ factor.
Notice that the final expression on the right-hand side of \eqref{e:loop-partition}
makes sense for any $N$ and equals $1$ when $n = 0$.

The two-point function for the $O(n)$ model can be defined analogously to
\eqref{e:two-point-function-phi4} and \eqref{e:Ising-2pt}. By a similar expansion
as was used to study the partition function above, the numerator in the two-point
function becomes
\begin{equation}
\label{e:2pt-num}
n^{-1} \int d\sigma (\sigma_a \cdot \sigma_b) \prod_{xy\in\edges} e^{\beta\sigma_x\cdot\sigma_y}
	\approx
n^{-1}
\sum_{E\subset\edges} \beta^{|E|}
\int d\sigma (\sigma_a \cdot \sigma_b)
\prod_{xy\in E} \sigma_x \cdot \sigma_y.
\end{equation}
Once again, every vertex must appear twice on the right-hand side in order to make a
non-zero contribution to the sum. Due to the presence of the factor $\sigma_a \cdot \sigma_b$,
this means (unless $a = b$) that the sum can be replaced by a sum over subsets $E$ containing
a self-avoiding walk from $a$ to $b$ together with with a (possibly empty) family of mutually
avoiding self-avoiding loops that also avoid this walk. (As a very simple example, if $a \sim b$,
then there is a non-zero contribution from $E = \{ a, b \}$.) For any such configuration $E$
containing $N$ loops,
\begin{equation}
\int d\sigma \; (\sigma_a \cdot \sigma_b) \prod_{xy\in E} \sigma_x \cdot \sigma_y
	=
n^{1 + N}.
\end{equation}
The extra factor of $n$ arises from the walk in $E$ but is
cancelled by the normalization in \eqref{e:2pt-num}.
Thus, after formally setting $n = 0$ (so that $Z = 1$), the two-point function
is approximately given by
\begin{equation}
1 + \sum_{\omega\in\Scal_n(a, b)} \beta^{|\omega|},
\end{equation}
which is the two-point function (i.e.\ generating function) for self-avoiding
walk.
% Thus, the two-point function is approximately
% \begin{equation}
% \frac{1}{1 + O(n)}
% \left(
% 	1
% 		+
% 	\sum_{\omega : a \to b} \beta^{|\omega|}
% 		+
% 	O(n)
% \right).
% \end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Self-avoiding walk representation}
% This section based on saw-sa
\label{sec:intrep}

In this section we describe an integral representation of the of WSAW-SA
% which is a special case of a result of Brydges, Imbrie, and Slade \cite{BIS09}.
% We restrict out attention to
on the discrete torus $\Lambda$. We begin with the necessary
background on Grassmann integration, introduced in \cite{Bere66}. However, we
follow the treatment of \cite{BIS09}.

\subsubsection{Boson and fermion fields}
\label{sec:forms}

Let $\phi_x$, $\bar\phi_x$ denote complex variables indexed by $x\in\Lambda$.
We refer to $(\phi, \phib)$ as a \emph{boson} field. Let $u_x, v_x$ denote
the real and imaginary parts of $\phi_x$ and define the differentials
$d\phi_x = du_x + i dv_x$ and likewise for $d\phib_x$.
We multiply differential forms in the usual way via the anticommutative wedge product
$\wedge$ but drop this in our notation; in particular,
\begin{equation}
d\phib_x d\phi_x = 2 i du_x dv_x.
\end{equation}

\begin{example}
Let $C$ be a positive-definite symmetric $\Lambda\times\Lambda$ matrix. The
\emph{complex Gaussian measure} with covariance $C$ is the probability measure
on $\R^{2\Lambda}$ given by
\begin{equation}
d\mu_C(\phi, \phib)
	=
\frac{d\phib d\phi}{\det(2\pi i C)} e^{-\phi \cdot A \phib}
\end{equation}
where $A = C^{-1}$ and
\begin{equation}
d\phib d\phi \coloneqq \prod_{x\in\Lambda} d\phib_x d\phi_x
\end{equation}
The order in which the product over $x\in\Lambda$ is taken does not matter
since the $d\phib_x d\phi_x$ commute. The complex Gaussian satisfies a
version of Wick's theorem. In particular,
\begin{equation}
\label{e:wick-complex2}
\int \phib_x \phi_y \; d\mu_C(\phi, \phib) = C_{xy}.
\end{equation}
\end{example}

Let
\begin{equation}
\psi_x = \frac{1}{\sqrt{2\pi i}} d\phi_x,
\quad
\bar\psi_x = \frac{1}{\sqrt{2\pi i}} d\bar\phi_x,
\end{equation}
where we fix a choice of complex square root. We refer to $(\psi_x, \psib_x)_{x\in\Lambda}$
as a \emph{fermion} field.
A differential form that is the
product of a function of $(\phi, \bar\phi)$
with $p$ differentials is said to have \emph{degree} $p$.
A sum of forms of even degree is said to be \emph{even}.

We introduce a copy $\bar\Lambda$ of $\Lambda$
and we denote the copy of $X \subset \Lambda$ by $\bar X \subset \bar\Lambda$.
We also denote the copy of $x \in \Lambda$
by $\bar x \in \bar\Lambda$ and define $\phi_{\bar x} = \bar\phi_x$ and $\psi_{\bar x} = \bar\psi_x$.
Then any differential form $F$ can be written
\begin{equation}
\lbeq{FinNcal}
F
=
\sum_{\vec y}
F_{\vec y} (\phi, \bar\phi)
\psi^{\vec y}
\end{equation}
where the sum is over finite sequences $\vec y$ over $\Lambda\sqcup\bar\Lambda$,
and $\psi^{\vec y} = \psi_{y_1} \ldots \psi_{y_p}$
% (in some canonical order)
when $\vec y = (y_1, \ldots, y_p)$. Here, we take the sequences to be ordered in
some canonical fashion. When $\vec y = \varnothing$ is the empty sequence,
$F_\varnothing$ denotes the $0$-degree (bosonic) part of $F$.

In order to apply the results of \cite{BBS-saw4-log,BBS-saw4,BSTW-clp}, we require
smoothness of the coefficients $F_{\vec y}$ of $F$.  For Theorem~\ref{thm:mr}(i,ii),
we need these coefficients to be $C^{10}$, and for Theorem~\ref{thm:mr}(iii) we require
a $p$-dependent number of derivatives for the analysis of $\xi_p$, as discussed in \cite{BSTW-clp}.
In either case, we let $p_\Ncal$ denote the desired degree of smoothness.
We will discuss this further in Section~\ref{sec:newnorm}.

We let $\Ncal^\varnothing$ be the algebra of even forms with sufficiently smooth coefficients
and we let $\Ncal^\varnothing(X) \subset \Ncal^\varnothing$ be the sub-algebra of even forms only depending on fields
in $X$. Thus, for $F \in \Ncal^\varnothing(X)$, the sum in \eqref{e:FinNcal} runs over sequences $\vec y$
over $X \sqcup \bar X$.

Now let $F = (F_j)_{j \in J}$ be a finite collection of even forms
indexed by a set $J$
and write $F_\varnothing = (F_{\varnothing,j})_{j \in J}$.
Given a $C^\infty$ function $f : \R^J \to \C$, we define
$f(F)$ by its Taylor expansion about $F_\varnothing$:
\begin{equation}
f(F) = \sum_\alpha \frac{1}{\alpha!} f^{(\alpha)}(F_\varnothing) (F - F_\varnothing)^\alpha.
\end{equation}
The summation terminates as a finite sum, since $\psi_x^2 = \bar\psi_x^2 = 0$
by anticommutativity.
% due to the anti-commut\-ative product.

We define the integral $\int F$ of a differential form $F$ in the usual way
as the Riemann integral of its top-degree part (which may be regarded as a function
of the boson field).
In particular, given a positive-definite symmetric
$\Lambda \times \Lambda$ matrix $C$ with inverse $A = C^{-1}$,
we define the \emph{Gaussian expectation} (or \emph{super-expectation}) of $F$ by
\begin{equation}
\lbeq{ExCF}
\Ex_C F = \int e^{-S_A} F,
\end{equation}
where
\begin{equation}
\label{e:action}
S_A = \sum_{x\in\Lambda} \Big(\phi_x (A\bar\phi)_x + \psi_x (A \bar\psi)_x\Big).
\end{equation}
% Note that the computation of \eqref{e:ExCF} always reduces to an integral of the form
% \begin{equation}
% \int f(\phi, \phib) \psi^{\Lambda\sqcup\bar\Lambda},
% \end{equation}
% where $\psi^{\Lambda\sqcup\bar\Lambda}$ denotes the product of all the fermionic fields
% in their canonical ordering. Thus, in order to make the change of variables
% $\psi_x \mapsto a \psi_x$ for some $x$ we must simply scale the integral by the factor
% $a^{-1}$. This is the opposite effect of a bosonic change of variables $\phi_x \mapsto a \phi_x$
The super-expectation possesses the remarkable property that
\begin{equation}
\label{e:tau-iso}
\int e^{-S_A} F(\tau) = F(0).
\end{equation}
In particular,
\begin{equation}
\label{e:self-normal}
\int e^{-S_A} = 1.
\end{equation}
Moreover, if $F$ is a degree-$0$ form, then
\begin{equation}
\Ex_C F = \int F \; d\mu_C.
\end{equation}
There is also a version of Wick's theorem for fermions. In particular,
\begin{equation}
\label{e:wick-fermion2}
\int e^{-S_A} \psi_x \psib_x = C_{xx}.
\end{equation}

For $F = f(\phi, \bar\phi) \psi^{\vec y}$, we let
\begin{equation}
\theta F = f(\phi + \xi, \bar\phi + \bar\xi) (\psi + \eta)^{\vec y},
\end{equation}
where $\xi$ is a new boson field, $\eta = (2\pi i)^{-1/2} d\xi$ a new fermion field,
and $\bar\xi, \bar\eta$ are the corresponding conjugate fields.
We extend $\theta$ to all $F \in \Ncal^\varnothing$ by linearity
and define the convolution operator $\Ex_C\theta$ by letting
$\Ex_C\theta F \in \Ncal^\varnothing$ denote the Gaussian expectation of $\theta F$ with respect
to $(\xi, \bar\xi, \eta, \bar\eta)$, with $\phi,\phib,\psi,\psib$ held fixed.

\subsubsection{Integral representation of the two-point function}
\label{sec:Gintrep}

An integral representation formula applying to general local time functionals
is given in \cite{BEI92,BIS09}. We state the result we need in the proposition below.
A direct proof can be obtained by a small modification to the proof in
\cite[Appendix~A]{ST-phi4}.

We define the differential forms:
\begin{align}
\label{e:taudef}
\tau_x
	&=
\phi_x \bar\phi_x + \psi_x \bar\psi_x
	\\
\label{e:addDelta}
\tau_{\Delta,x}
	&=
\frac 12
\Big(
	\phi_{x} (- \Delta \bar{\phi})_{x} + (- \Delta \phi)_{x} \bar{\phi}_{x}
		+
	\psi_{x}  (- \Delta \bar{\psi})_{x} + (- \Delta \psi)_{x}  \bar{\psi}_{x}
\Big)
	\\
\label{e:nablatau}
|\nabla \tau_x|^2
	&=
\sum_{|e|=1} (\nabla^e \tau)_x^2.
\end{align}
Recall \eqref{e:Udef-pos} and define
\begin{equation}
\label{e:Vdef2}
V_{\gcc,\gamma,\nu,N}
	=
U_{\gcc,\gamma}(\tau)
	+
\sum_{x\in\Lambda_N}
\Big(
	\nu \tau_x + \tau_{\Delta,x}
\Big)
% \sum_{x\in\Lambda_N}
% \Big(
% 	\gcc \tau_x^2 + \nu \tau_x + \tau_{\Delta,x} - \tfrac{1}{2 d} \gamma |\nabla \tau_x|^2
% \Big)
\end{equation}

\begin{prop}
Let $d > 0$ and $\gcc > 0$. For $\gamma < \gcc$ and $\nu \in \R$,
\begin{equation}
\label{e:Grep-pos-bis}
G_{x,N}(\gcc, \gamma, \nu; 0)
	=
\int e^{-V_{\gcc,\gamma,\nu,N}} \phib_0 \phi_x.
% \int e^{-U_{\gcc,\gamma,\nu,N}} \bar\phi_a \phi_b.
\end{equation}
\end{prop}

\subsubsection{Finite-volume approximation}

In order to make use of the integral representation above, we must approximate the
WSAW-SA on $\Zd$ by a model on $\Lambda_N$.

Let $X^{L^N}$ denote the simple random walk on $\Lambda_N$.
For $F_T = F_T(X)$ any one of the functions $L_T^x,I_T,C_T$
of $X$ defined in \eqref{e:LTx-def}--\eqref{e:CTdef},
we write $F_{N,T} = F_T(X^{L^N})$. For instance, with $n=L^N$,
\begin{equation}
    L^x_{N,T} = \int_0^T \1_{X^{n}_t=\;x} \; dt,
    \quad I_{N,T} = \sum_{x \in \Lambda_N}(L_{N,T}^x)^2 .
\end{equation}

As before, we identify the vertices of $\Lambda_N$ with nested subsets of $\Zd$,
centred at the origin (approximately if $L$ is even),
with $\Lambda_{N+1}$ paved by $L^d$ translates of $\Lambda_N$.
% We can thus define $\partial \Lambda_N$ to be the inner vertex boundary of $\Lambda_N$.
We denote the expectation of $X^{L^N}$ started from $0 \in \Lambda_N$ by $E^{\Lambda_N}_0$
and define
\begin{align}
\label{e:cN}
c_{N,T}(x)
    &= E^{\Lambda_N}_0 \left( e^{-U_{\gcc,\gamma,T}} \1_{X(T)=b} \right),
    \quad x \in \Lambda_N \\
c_{N,T}
    &= E^{\Lambda_N}_0 \left( e^{-U_{\gcc,\gamma,T}} \right).
\end{align}
The finite-volume two-point function and susceptibility
are defined by
\begin{align}
G_{x,N}(\gcc,\gamma,\nu; 0)
    &=
\int_0^\infty c_{N,T}(x) e^{-\nu T} \; dT, \\
\label{e:chiNdef-pre}
\chi_N(\gcc, \gamma, \nu; 0)
    &=
\int_0^\infty c_{N,T} e^{-\nu T} \; dT.
\end{align}
The proof of the following proposition is given in Appendix~\ref{sec:finvol}.

\begin{prop}
\label{prop:finvol}
Let $d >0$, $\gcc >0$ and $\gamma < \gcc$. For all $\nu \in \R$,
\begin{equation}
\label{e:Givlc}
\lim_{N \to \infty}
G_{x,N}(\gcc,\gamma,\nu; 0)
=
G_x(\gcc,\gamma,\nu; 0)
\end{equation}
and
\begin{equation}
\label{e:chilim-pre}
\lim_{N\to\infty}\chi_N(\gcc,\gamma,\nu; 0) =   \chi(\gcc,\gamma,\nu; 0).
\end{equation}
In fact, $\chi_N$ and $\chi$ are analytic in ${\rm Re} \nu > \nu_c$ and
$\chi_N \to \chi$ uniformly on compact subsets of this domain.
\end{prop}
